Incentivizing Exploration with Unbiased History

### 2018-10-24 2level.tex
refactor
stuff

  The key idea behind the policy is that the first level effectively
  boosts the exploration probability of Greedy. Since each run of
  \ALGG explores all arms with constant probability (Lemma
  \ref{lem:greedy}), by simulating multiple runs of Greedy, we can
  ensure that with high probability, every arm is pulled with a
  sufficient number of times. As a result, every agent in the second
  level will pull an arm with mean rewards close to the optimal.

@@

@@

@@

% \begin{itemize}
  \paragraph{Concentration of the number of arm $a$ pulls in the first
    level.}
  By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$. Define
  $W_1^a$ to be the event that the number of arm $a$ pulls in the
  first level is at least $q_a T_1- \GdT \sqrt{T_1\log(T)}$.
  \swedit{As long as we set $T_1 \geq \frac{4\GdT^2}{\GdP^2}\log(T)$,
    this implies that the number of arm $a$ pulls is then at least
    $q_a T_1/2$.}  By Chernoff bound,
  \[
    \Pr[W_1^a] \geq 1-\exp(-2\log(T)) \geq 1-1/T^2.
  \]
Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a}W_1^a$). By union bound, we have
\[
\Pr[W_1] \geq 1- \frac{K}{T^2} \geq 1 - \frac{1}{T}.
\]
\paragraph{Concentration of the empirical mean of arm $a$ pulls in the first level.}
To facilitate our reasoning, let us imagine there is a tape of length
$T$ for each arm $a$, with each cell containing an independent draw of
the realized reward from the distribution Ber$(\mu_a)$. Then for each
arm $a$ and any $N\in [T]$, we can think of the sequence of the first
$N$ realized rewards of $a$ coming from the prefix of $N$ cells in its
reward tape. Define $W^{a,t}_2$ to be the event that the empirical
mean of the first $t$ \swedit{realized rewards in the tape} of arm $a$
is at most $\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$. Define $W_2$
to be the intersection of these events (i.e.
$\bigcap_{a,t} W^{a,t}_2$).  By Chernoff bound,\swcomment{$t$ may be
  confusing here}
\[
\Pr[W^{a,t}_2] \geq 1 - 2\exp(-4\log(T)) \geq 1-2/T^4.
\]
By union bound, 
\[
\Pr[W_2] \geq 1 - KT \cdot \frac{2}{T^4} \geq 1 - \frac{2}{T}.
\]

>>>>

  The key idea behind the policy is that the first level effectively
  boosts the exploration probability of Greedy. Since each run of
  \ALGG explores all arms with constant probability (Lemma
  \ref{lem:greedy}), by simulating multiple runs of Greedy, we can
  ensure that with high probability, every arm is pulled with a
  sufficient number of times. The following Lemma follows from
  applying Chernoff bound and union bound.

@@

\begin{lemma}[Concentration of arm pulls]\label{lem:t1runs}
  Consider $T_1$ indepdent runs of \ALGG of length $T_G$. Let $N_a$ be
  the number of arm $a$ pulls among all runs. Then with probability at
  least $1-\delta$, for all $a\in \A$,
  \[
    \left| N_a - q_a T_1\right| \leq T_G \sqrt{T_1 \log(2K/\delta) / 2}
  \]
\end{lemma}

@@

\swedit{As a result, every agent in the second level will pull an arm
  with mean rewards close to the optimal, which gives us the following
  regret guarantee.}

@@

% \begin{itemize}
  \paragraph{Concentration of the number of arm $a$ pulls in the first
    level.}
  \OMIT{By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$.}
  Define $W_1^a$ to be the event that the number of arm $a$ pulls in
  the first level is at least $q_a T_1- \GdT \sqrt{T_1\log(T)}$.
  \swedit{As long as we set $T_1 \geq \frac{4\GdT^2}{\GdP^2}\log(T)$,
    this implies that the number of arm $a$ pulls is then at least
    $q_a T_1/2$.} 
\OMIT{  By Chernoff bound,
  \[
    \Pr[W_1^a] \geq 1-\exp(-2\log(T)) \geq 1-1/T^2.
  \]
}
Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a}W_1^a$). By \Cref{lem:t1runs}, we have
\[
\Pr[W_1] \geq 1- \frac{K}{T^2} \geq 1 - \frac{1}{T}.
\]
\paragraph{Concentration of the empirical mean of arm $a$ pulls in the first level.}
To facilitate our reasoning, let us imagine there is a tape of length
$T$ for each arm $a$, with each cell containing an independent draw of
the realized reward from the distribution Ber$(\mu_a)$. Then for each
arm $a$ and any $N\in [T]$, we can think of the sequence of the first
$N$ realized rewards of $a$ coming from the prefix of $N$ cells in its
reward tape. Define $W^{a,t}_2$ to be the event that the empirical
mean of the first $t$ \swedit{realized rewards in the tape} of arm $a$
is at most $\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$. Define $W_2$
to be the intersection of these events (i.e.
$\bigcap_{a,t} W^{a,t}_2$).  By Chernoff bound,\swcomment{$t$ may be
  confusing here}
\[
\Pr[W^{a,t}_2] \geq 1 - 2\exp(-4\log(T)) \geq 1-2/T^4.
\]
By union bound, 
\[
\Pr[W_2] \geq 1 - KT \cdot \frac{2}{T^4} \geq 1 - \frac{2}{T}.
\]
